---
title: "Multiple Comparison Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(rsconnect)
rsconnect::setAccountInfo(name='jesseweinstein', token='6A12373F2B73A1C1C003102D3643723E', secret='g6EEt5F4F0AT54ZJ5yOev0q+8yLStV9PLk6YOOdS')
knitr::opts_chunk$set(echo = FALSE)
```


## Multiple Comparisons 

### Welcome

This tutorial will teach you how to multiple comparison procedure in order to compare characteristics of different groups represented by a nominal facor. This tutorial will be using the package "Multcomp" in order to help with these comparisons.  

In order to help teach these skills we will be using the "alpha" data set which can be found in the Coin package. This data set found longer alleles of NACP-REP1 in alcohol-dependent patients and report that the allele lengths show some association with levels of expressed alpha synuclein mRNA in alcohol-dependent subjects. In this data set we will be comparing the distribution of the expression level of alpha synuclein mRNA in three groups of subjects defined by the allele length.


The packages and data needed for this code are :

```{r packages, echo=TRUE}
library(coin)
library(multcomp)
library(sandwich)
alphas <- data.frame(alpha)

```


## Compare data using glht()
glht() creates a General linear hypotheses and multiple comparison for parametric models. 
In glht() you will include a fitted model, as well as a specification of the linear hypothesis to be tested. 

### Formatting your data to use glht()
The first thing that we must do is format our data in order to use glht(). To do this we will start off bi fitting a simple one-way ANOVA model to our data. We must also create a matrix K in order to contain the 3 group differences. We will do this using the aov and mcp functions.
```{r format, echo = TRUE}

amod <- aov(elevel ~ alength, data = alphas)
Tukey <- mcp(alength = "Tukey")

```
Once you have all of your data in the correct formal you are ready to use glht()
```{r calculations, echo=TRUE}
 amod_glht <- glht(amod, linfct = mcp(alength = "Tukey"))
 amod_glht$linfct

```

The amod_glht object now contains information about the estimated linear function ϑˆ and their covariance matrix.


## Analyzing the data
In order to analyze the matrix that you have created functions such as the coef(), vcov(), summary(), and confint() can be used. Both the summary(), and confint() functions are used in order to compute summary statistics such as pvalues and confidence intervals. We can also use the sandwhich function in order to estimate the covariance matrix.

```{r, echo=TRUE}
coef(amod_glht)
vcov(amod_glht)
summary(amod_glht)
confint(amod_glht)

amod_glht_sw <- glht(amod, linfct = mcp(alength = "Tukey"),  vcov = sandwich)
summary(amod_glht_sw)


```


## Graphing the data

We will now graph the confidence intervals of the data based on both the ordinary matrix as well as the sandwhich estimator. 

```{r, echo=TRUE}
par(mfrow = c(1, 1))
confidence1 <- confint(glht(amod, linfct = mcp(alength = "Tukey")))
confidence2 <- confint(glht(amod, linfct = mcp(alength = "Tukey"), vcov = sandwich))
ex1 <- expression(paste("Tukey (ordinary", bold(S)[n],")"))
ex2 <- expression(paste("Tukey (sandwich", bold(S)[n],")"))

plot(confidence1, xlim = c(-0.6, 2.6), main = ex1, xlab = "Difference", ylim = c(0.5, 3.5))
plot(confidence2, xlim = c(-0.6, 2.6), main = ex2, xlab = "Difference", ylim = c(0.5, 3.5))




library(rsconnect)


```

